Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-11 doc/report/msc-report.tex
minor fixes in bigtable section.

BigTable is a data store designed for traversal of very large data sets.
BigTable's cells are basically indexed by row key, column key, and a time-stamp.
Each row has a key and any number of cells attached to it. The rows in a table
are sorted by their keys. The typical use-case of BigTable is to scan a range of
rows. It is therefor important to set up the row keys so that related data is
close to each other. For example, if it makes sense to traverse the data in
chronological order, the key might contain a representation of the data's
time-stamp. The classic example is to have the reversed domain name (i.e.
com.google.www) as the row key, which means that all sub-domains of any domain
are next to each other (see table 2.1).

@@

BigTable's data model can indeed be thought of as a sparse distributed
multidimensional sorted map. In concept, this multidimensional map is identical
to a nested hash table. The dimensions of this multidimensional map is mapped
out on the row key, the column family and the column qualifier, and possibly
also of the version time-stamp.

@@

The data model is a simple one: Rows of data are stored in labeled tables. Each
row is indexed with a row key, a column key, and a time-stamp. The columns have
the form "column-family:qualifier", where the column-family is one of a number
of fixed column-families defined by the table's schema, and the qualifier is an
arbitrary string specified by the application. In effect, column-families are
pre-announced when creating the table while qualifiers are not. The contents of
each column family are stored together, so the user will want to store items
that have similar characteristics in the same column family.  Each data point is
called a cell. A cell is an uninterpreted array of bytes, there are no data
types, and it is up to the application to interpret the data correctly. The
table can store any number of time-stamped versions of each cell, allowing
versioning of data.

>>>>

BigTable is a data store designed for storing very large data sets. BigTable's
cells are basically indexed by row key, column key, and a time-stamp. Each row
has a key and any number of cells attached to it. The rows in a table are sorted
by their keys. The typical use-case of BigTable is to scan a range of rows. It
is therefor important to set up the row keys so that related data is close to
each other. For example, if it makes sense to traverse the data in chronological
order, the key might contain a representation of the data's time-stamp. The
classic example is to have the reversed domain name (i.e. com.google.www) as the
row key, which means that all sub-domains of any domain are next to each other
(see table 2.1).

@@

BigTable's data model can indeed be thought of as a sparse, distributed, sorted,
multidimensional map. In concept, this multidimensional map is identical to a
nested hash table. The dimensions of the map are: row key, column family and
column qualifier, and a version time-stamp.

@@

The data model is a simple one: Rows of data are stored in labeled tables. Each
row is indexed with a row key, a column key, and a time-stamp. The column keys have
the form "column-family:qualifier", where the column-family is one of a number
of fixed column-families defined by the table's schema, and the qualifier is an
arbitrary string specified by the application. In effect, column-families are
pre-announced when creating the table while qualifiers are not. The contents of
each column family are stored together, so the user will want to store items
that have similar characteristics in the same column family.  Each data point is
called a cell. A cell is an uninterpreted array of bytes, there are no data
types, and it is up to the application to interpret the data correctly. The
table can store any number of time-stamped versions of each cell, allowing
versioning of data.
